\textit{What is a PhD Thesis?} 

Your thesis is a research report. The report concerns a problem or series of problems in your area of research and it should describe what was known about it previously, what you did towards solving it, what you think your results mean, and where or how further progress in the field can be made

\textbf{Thinking}
\begin{itemize}
\item Add description of special words. E.g.: Interlocutor, Lecixal Entrainment, Morphology, ...
\item
\end{itemize}

\textbf{Chapters Thinking}
Think about how I got from one point to the other. I started out with the ash experiment. during this experiment I learned that/thought that humans don't see robots as their peers. Therefore robots don't influence humans (Sidenote: Check out Clay+Peters follow up paper about How/Why people need more than just someone sitting next to them to be influenced). It's also important to mention that I have a general focus on a group of robots. One-on-one is probably not where the future will be heading too. After I learned that humans don't see robots as their peers I had to change strategy. I stated designing a general experimental setup were I can test different persuasive techniques. All under the assumption that the human and robot are peers or at least work together. The problem however, with this setup was that I can only test the robots influence on a couple of people. Maximul 5 or so. To actually see how all of this would influence a population I had to simulate it. To do this simulation I extended Janets agent based model with robot nodes. Important was that I used the update strategy I have learned from the previous experiment so the simulation would give as plausible results. Depeding on the different strategies the robots used in the lab experiments the simulation would end up with different results. 
In a future part, I would like to try the simulation in an actual study. It is probably not doable at the university level but maybe a company would let me do research on their users.
